---
title: "Exploratory Analysis"
output: html_document
---
```{r}
library(lsa)
library(splitstackshape)
df1 <- read.csv('/home/Shalini/Desktop/SEM 5/DA/Project/Datasets/bgg_db_2018_01.csv')
df2 <- read.csv('/home/Shalini/Desktop/SEM 5/DA/Project/Datasets/bgg_db_2017_04.csv')
df3 <- read.csv('/home/Shalini/Desktop/SEM 5/DA/Project/Datasets/bgg_db_1806.csv')
```
```{r}
setwd()
```
```{r}
df1 <- df1[order(df1$rank), ]
Rank_df1 <- df1

```
Splitting Mechanic and Categorical Variables
```{r}
catSplit1 <- cSplit(Rank_df1, "category", ",")
catSplitDummy <- Rank_df1
for (i in 1:nrow(catSplit1)){
  for(j in 21:27){
    if(!is.na(catSplit1[i,as.numeric(j)]))
    {
      cat <- as.character(catSplit1[[i,as.numeric(j)]])
      cat_col <- paste("catSplit", cat, sep = "_")
      catSplitDummy[i, cat_col]<-1
    }
  }
}
catSplitDummy$catSplit_NA <- NULL
catSplitDummy[is.na(catSplitDummy)] <- 0


mechSplit1 <- cSplit(Rank_df1, "mechanic", ",")
mechSplitDummy <- Rank_df1
for (i in 1:nrow(mechSplit1)){
  for(j in 21:27){
    if(!is.na(mechSplit1[i,as.numeric(j)]))
    {
      mech <- as.character(mechSplit1[[i,as.numeric(j)]])
      mech_col <- paste("mechSplit", mech, sep = "_")
      mechSplitDummy[i, mech_col]<-1
    }
  }
}
mechSplitDummy$mechSplit_NA <- NULL
mechSplitDummy[is.na(mechSplitDummy)] <- 0
DummyDataFrame <- merge(catSplitDummy, mechSplitDummy, by = colnames(df1))
DummyDataFrame <- subset(DummyDataFrame, select = -c(bgg_url, names, image_url, mechanic, category, designer))
```

```{r}
#Seeing which mechanics are the most common and which can be dropped
Mech_2018 <- DummyDataFrame %>% select(starts_with('mechSplit_'))
p3 <- plot_ly(x = colnames(Mech_2018), y = colSums(Mech_2018), name = "Mechanics in 2018", type = "bar")  %>% 
        layout(title = "Mechanics in 2018")
c_2018 <- colSums(Mech_2018)
p3
```

Dropping mechanics that occur in less than 150 games
```{r}
LeastCommonMech <- names(c_2018[c_2018<150]) 
LeastCommonMech
```
Dropping the above columns from the Dummy variable data frame
```{r}
LeastCommonMechIndex <- match(LeastCommonMech, colnames(DummyDataFrame))
DummyDataFrame[LeastCommonMechIndex] <- NULL
colnames(DummyDataFrame)
```
Applying same steps for categories
```{r}
Cat_2018 <- DummyDataFrame %>% select(starts_with('catSplit_'))
p_cat <- plot_ly(x = colnames(Cat_2018), y = colSums(Cat_2018), name = "Categories in 2018", type = "bar")  %>% 
        layout(title = "Categories in 2018")
cat_2018 <- colSums(Cat_2018)
p_cat
```

Dropping categories that occur in less than 150 games
```{r}
LeastCommonCat <- names(cat_2018[cat_2018<150]) 
LeastCommonCat
```
Dropping the above columns from the Dummy variable data frame
```{r}
LeastCommonCatIndex <- match(LeastCommonCat, colnames(DummyDataFrame))
DummyDataFrame[LeastCommonCatIndex] <- NULL
colnames(DummyDataFrame)
```

Remove any games that don't contain those categories or mechanics anymore
```{r}
Final <- DummyDataFrame[apply(DummyDataFrame[c(15:53)],1,function(z) !all(z==0)),]
Final <- Final[apply(Final[c(15:33)],1,function(z) !all(z==0)),]
Final <- Final[apply(Final[c(34:53)],1,function(z) !all(z==0)),]

```
So now we have a dimensionally reduced dataset that we will write to a csv
```{r}
write.csv(Final, "/home/Shalini/Desktop/SEM 5/DA/Project/MuffyNom/FixedGames.csv")
```

